---
title: "MOFA Downstream"
output: html_document
author: Eric Zillich, adapted from https://raw.githack.com/bioFAM/MOFA2_tutorials/master/R_tutorials/CLL.html and https://raw.githack.com/bioFAM/MOFA2_tutorials/master/R_tutorials/getting_started_R.html
date: last modification 2024-04-04
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages and python, include=FALSE}
library(MOFA2)
library(MOFAdata)
library(data.table)
library(ggplot2)
library(tidyverse)
library(psych)
library(ggpubr)
library(dplyr)
library(clusterProfiler)
library(enrichplot)
library(DOSE)
library(org.Hs.eg.db)


reticulate::use_python("/anaconda3/bin/python", required=TRUE)
```

# Import the model and merge with metadata
```{r import}
BA9 <- readRDS("/MOFA_dir/output/MOFA_BA9_trained_model_20240102.rds")


# metadata
pheno_meth_expr <- read.delim("/MOFA_dir/input/pheno_meth_expr.txt")
colnames(pheno_meth_expr)[1] <- "sample"
pheno_meth_expr$sample <- as.character(pheno_meth_expr$sample)

samples_metadata(BA9) <- pheno_meth_expr
```


# Inspect the model characteristics
Check if factors are largely uncorrelated
```{r check if factors are largely uncorrelated}
plot_factor_cor(BA9)

```
Variance decomposition analysis
```{r variance decomposition analysis}
p1 <- plot_variance_explained(BA9)
ggsave("/MOFA_dir/model_factors.pdf",p1, width = 4, height = 5)
 
```

Total variance explained per view
```{r total variance explained per view}
p2 <- plot_variance_explained(BA9, plot_total = T)[[2]]
ggsave("/MOFA_dir/model_varexp.pdf",p2, width = 5, height = 4)
 
```


# Factor characterization 
How are the factors related to molecular processes?
Association with sample metadata
- Factor values
- Feature weights
- GSEA on mRNA weights


# Association with sample metadata
```{r association with sample metadata}

p3 <- correlate_factors_with_covariates(BA9, abs=F,
  covariates = colnames(pheno_meth_expr[c("RIN","CUD","pH","Age","PMI","Axis_1_Dependence","Simplified_Axis_1")]), 
  plot="log_pval"
)
ggsave("/MOFA_dir/model_cor_cov.pdf",p3, width = 3, height = 5)


metadata <- samples_metadata(BA9)
rownames(metadata) <- metadata$sample
f9 <-get_factors(BA9, factors = 9, as.data.frame = FALSE)

meta2 <- merge(metadata,f9$group1,by=0 )
cor <- psych::corr.test(meta2$Factor9 , meta2$CUD, method = "pearson", 
        adjust = "BH")
cor$r #-0.4773093
cor$p #0.01583205

cor2 <- psych::corr.test(meta2$Factor9 , meta2$Age, method = "pearson", 
        adjust = "BH")
cor2$r #0.4698416
cor2$p #0.01779693


wilcox.test(meta2$Factor9[meta2$CUD==1],meta2$Factor9[meta2$CUD==0])#p-value = 0.022
```


# Plot feature weights
```{r plot feature weights}
# Score for each feature on each factor -> large values for features having strong associations with a factor
plot_weights(BA9,
 view = "Meth",
 factor = 9,
 nfeatures = 10,     # Top number of features to highlight
 scale = T           # Scale weights from -1 to 1
)

p4 <- plot_top_weights(BA9,
 view = "Meth",
 factor = 9,
 nfeatures = 10,     # Top number of features to highlight
 scale = T           # Scale weights from -1 to 1
)
ggsave("/MOFA_dir/meth_topweights.pdf",p4, width = 5, height = 4)

plot_weights(BA9,
 view = "Expr",
 factor = 9,
 nfeatures = 10,     # Top number of features to highlight
 scale = T           # Scale weights from -1 to 1
)

p5 <- plot_top_weights(BA9,
 view = "Expr",
 factor = 9,
 nfeatures = 10,     # Top number of features to highlight
 scale = T           # Scale weights from -1 to 1
)
ggsave("/MOFA_dir/expr_topweights.pdf",p5, width = 5, height = 4)

# Export weight information 
Expr_weights <- get_weights(BA9,views = "Expr",factor=9)
Expr_weights <- as.data.frame(Expr_weights$Expr)
Expr_weights$Gene <- rownames(Expr_weights)
Expr_weights <- Expr_weights[order(Expr_weights$Factor9,decreasing = T),]
Expr_weights <- Expr_weights[,c(2,1)]
write.table(Expr_weights,"/MOFA_dir/expr_weights_factor9.txt",sep=" ",quote=F,row.names = F,col.names = T)


Meth_weights <- get_weights(BA9,views = "Meth",factor=9)
Meth_weights <- as.data.frame(Meth_weights$Meth)
Meth_weights$CpG <- rownames(Meth_weights)
Meth_weights <- Meth_weights[order(Meth_weights$Factor9,decreasing = T),]
Meth_weights <- Meth_weights[,c(2,1)]
Meth_weights$CpG <- gsub(" - ","-",Meth_weights$CpG)
write.table(Meth_weights,"/MOFA_dir/Meth_weights_factor9.txt",sep=" ",quote=F,row.names = F,col.names = T)

```

# CUD status association with Factor 9
```{r plot CUD status association with Factor 1}
p6 <- plot_factor(BA9, 
  factors = 9, 
  color_by = "CUD",
  add_violin = TRUE,
  dodge = TRUE
)+ylim(-0.16,0.16)+scale_fill_manual(values=c("#268989","#E43F3F"))
ggsave("/MOFA_dir/f9_CUD.pdf",p6, width = 5, height = 4)

p7 <- plot_factor(BA9, 
  factors = 9, 
  color_by = "Age",
  add_violin = TRUE,
  dodge = TRUE
)
ggsave("/MOFA_dir/f9_age.pdf",p7, width = 4, height = 4)

```

```{r GSEA}
# Create input matrix for GSEA using GO BP terms for human
library(msigdbr)

# Extract the gene sets from the current GO BP repository to get the genes involved in the pathways
genesets = msigdbr(species = "human", category = "C5", subcategory = "BP") 

library(SAMBAR)
# convert the current GO BP gmt file from msigdb to a binary matrix with gene and geneset as columns and rows
gs <- convertgmt("/MOFA_dir/input/c5.go.bp.v2023.1.Hs.symbols.gmt",unique(genesets$gene_symbol))

# GSEA on positive weights, with default options
res.positive <- run_enrichment(BA9, 
  feature.sets = gs, 
  view = "Expr",
  sign = "positive"
)

# GSEA on negative weights, with default options
res.negative <- run_enrichment(BA9, 
  feature.sets = gs, 
  view = "Expr",
  sign = "negative"
)


plot_enrichment(res.positive, factor = 9, max.pathways = 25)

plot_enrichment_detailed(
  enrichment.results = res.positive,
  factor = 9, 
  max.pathways = 3
)

plot_enrichment(res.negative, factor = 9, max.pathways = 25)

plot_enrichment_detailed(
  enrichment.results = res.negative,
  factor = 9, 
  max.pathways = 3
)


# Extract enrichment results
pos_gsea1 <- as.data.frame(res.positive$set.statistics)
pos_gsea1$TERM <- rownames(pos_gsea1)
pos_gsea1 <- pos_gsea1[,c("TERM","Factor9")]
colnames(pos_gsea1)[2] <- "GSEA set statistic"
pos_gsea2 <- as.data.frame(res.positive$pval.adj)
pos_gsea2$TERM <- rownames(pos_gsea2)
pos_gsea2 <- pos_gsea2[,c("TERM","Factor9")]
colnames(pos_gsea2)[2] <- "padj"
pos_gsea <- merge(pos_gsea1,pos_gsea2,by="TERM")
pos_gsea <-pos_gsea[order(pos_gsea$padj,decreasing = F),]

neg_gsea1 <- as.data.frame(res.negative$set.statistics)
neg_gsea1$TERM <- rownames(neg_gsea1)
neg_gsea1 <- neg_gsea1[,c("TERM","Factor9")]
colnames(neg_gsea1)[2] <- "GSEA set statistic"
neg_gsea2 <- as.data.frame(res.negative$pval.adj)
neg_gsea2$TERM <- rownames(neg_gsea2)
neg_gsea2 <- neg_gsea2[,c("TERM","Factor9")]
colnames(neg_gsea2)[2] <- "padj"
neg_gsea <- merge(neg_gsea1,neg_gsea2,by="TERM")
neg_gsea <-neg_gsea[order(neg_gsea$padj,decreasing = F),]

write.table(pos_gsea,"/MOFA_dir/output/MOFA_pos_gsea.txt",sep=";",quote=F,row.names = F,col.names = T)
write.table(neg_gsea,"/MOFA_dir/output/MOFA_neg_gsea.txt",sep=";",quote=F,row.names = F,col.names = T)

# Visualize in waterfall plot
library(ggpubr)
pos_ES <- as.data.frame(res.positive$set.statistics)
pos_padj <- as.data.frame(res.positive$pval.adj)
neg_ES <- as.data.frame(res.negative$set.statistics)
neg_padj <- as.data.frame(res.negative$pval.adj)

# create dataframe for plotting for factor 9
f9_GSEA <- data.frame(TERM=rep("",times=30),ES=rep(0,times=30), p_adj=rep(0,times=30),weights=c(rep("positive weights",times=15),rep("negative weights",times=15)))

f9_GSEA$p_adj[1:15] <- pos_padj$Factor9[order(pos_padj$Factor9,decreasing = F)]
f9_GSEA$TERM[1:15] <- rownames(pos_padj[order(pos_padj$Factor9,decreasing = F),])[1:15]
f9_GSEA$p_adj[16:30] <- neg_padj$Factor9[order(neg_padj$Factor9,decreasing = F)]
f9_GSEA$TERM[16:30] <- rownames(neg_padj[order(neg_padj$Factor9,decreasing = F),])[1:15]

pos_terms <- pos_ES[rownames(pos_ES) %in% rownames(pos_padj[order(pos_padj$Factor9,decreasing = F),])[1:15],]
pos_terms <- pos_terms[match(rownames(pos_padj[order(pos_padj$Factor9,decreasing = F),])[1:15],row.names(pos_terms)),]
neg_terms <- neg_ES[rownames(neg_ES) %in% rownames(neg_padj[order(neg_padj$Factor9,decreasing = F),])[1:15],]
neg_terms <- neg_terms[match(rownames(neg_padj[order(neg_padj$Factor9,decreasing = F),])[1:15],row.names(neg_terms)),]

f9_GSEA$ES[1:15] <- pos_terms$Factor9
f9_GSEA$ES[16:30] <- -(neg_terms$Factor9)

# rename pathways and round pvals for plotting
f9_GSEA$TERM <-  gsub("GOBP_","",f9_GSEA$TERM)
f9_GSEA$TERM <-  gsub("_"," ",f9_GSEA$TERM)
f9_GSEA$TERM <-  tolower(f9_GSEA$TERM)
f9_GSEA$p_adj <- signif(f9_GSEA$p_adj, digits=3)
f9_GSEA$TERM[f9_GSEA$TERM == "atp synthesis coupled electron transport"] <- "ATP synthesis coupled electron transport"
f9_GSEA$TERM[f9_GSEA$TERM == "mitochondrial electron transport nadh to ubiquinone"] <- "mitochondrial electron transport NADH to ubiquinone"
f9_GSEA$sig <- rep("***",times=length(f9_GSEA$TERM))

library(Seurat)
f9_gsea_plot <- ggbarplot(f9_GSEA, x = "TERM", y = "ES",
          fill = "weights",               # change fill color by cyl
          color = "black",            # Set bar border colors to white
          sort.val = "desc",          # Sort the value in dscending order
          sort.by.groups = FALSE, 
          lab.size=4)+ylim(-12.5,12.5)+NoLegend()+xlab(NULL)+scale_fill_manual(values=c("#268989","#E43F3F"))+ylab("GSEA set statistic")+ geom_text(aes(y=2*abs(ES)/ES,label = sig), vjust = 0.8,hjust=0.3,size=8)+coord_flip()+theme_minimal() + theme(text=element_text(size=20))

ggsave("/MOFA_dir/GSEA_factor9_waterfall.pdf",f9_gsea_plot,width=14,height=10)

# Plot detailed enrichment results

# modify the MOFA function 
plot1 <- function (enrichment.results, factor, alpha = 0.1, max.genes = 5, 
                   max.pathways = 10, text_size = 3) 
{
  stopifnot(is.list(enrichment.results))
  stopifnot(length(factor) == 1)
  if (!is.numeric(factor)) {
    if (!factor %in% colnames(enrichment.results$pval)) 
      stop(paste0("No feature set enrichment calculated for ", 
                  factor))
  }
  foo <- reshape2::melt(enrichment.results$feature.statistics[, 
                                                              factor], na.rm = TRUE, value.name = "feature.statistic")
  foo$feature <- rownames(foo)
  feature.sets <- enrichment.results$feature.sets
  feature.sets[feature.sets == 0] <- NA
  bar <- reshape2::melt(feature.sets, na.rm = TRUE)[, c(1, 
                                                        2)]
  colnames(bar) <- c("pathway", "feature")
  bar$pathway <- as.character(bar$pathway)
  bar$feature <- as.character(bar$feature)
  baz <- reshape2::melt(enrichment.results$pval.adj[, factor], 
                        value.name = "pvalue", na.rm = TRUE)
  baz$pathway <- rownames(baz)
  baz <- baz[baz$pvalue <= alpha, , drop = FALSE]
  if (nrow(baz) == 0) {
    stop("No siginificant pathways at the specified alpha threshold. \n\n         For an overview use plot_enrichment_heatmap().")
  }
  else {
    if (nrow(baz) > max.pathways) 
      baz <- head(baz[order(baz$pvalue), ], n = max.pathways)
  }
  baz$pathway <- factor(baz$pathway, levels = baz$pathway[order(baz$pvalue, 
                                                                decreasing = TRUE)])
  foobar <- merge(foo, bar, by = "feature")
  tmp <- merge(foobar, baz, by = "pathway")
  tmp_filt <- top_n(group_by(tmp, pathway), n = max.genes, 
                    abs(feature.statistic))
  pathways <- unique(tmp_filt$pathway)
  df <- data.frame(pathway = pathways, nfeatures = rowSums(feature.sets, 
                                                           na.rm = TRUE)[pathways])
  df <- merge(df, baz, by = "pathway")
  df$pathway_long_name <- sprintf("%s\n (Ngenes = %d) \n (p-val = %0.2g)", 
                                  df$pathway, df$nfeatures, df$pvalue)
  tmp <- merge(tmp, df[, c("pathway", "pathway_long_name")], 
               by = "pathway")
  tmp_filt <- merge(tmp_filt, df[, c("pathway", "pathway_long_name")], 
                    by = "pathway")
  order_pathways <- df$pathway_long_name[order(df$pvalue, decreasing = TRUE)]
  tmp$pathway_long_name <- factor(tmp$pathway_long_name, levels = order_pathways)
  tmp_filt$pathway_long_name <- factor(tmp_filt$pathway_long_name, 
                                       levels = order_pathways)
  p <- ggplot(tmp, aes_string(x = "pathway_long_name", y = "feature.statistic")) + 
    geom_text_repel(aes_string(x = "pathway_long_name", y = "feature.statistic", 
                               label = "feature"), size = text_size, color = "black", 
                    force = 1, data = tmp_filt) + geom_point(size = 0.5, 
                                                             color = "lightgrey") + geom_point(aes_string(x = "pathway_long_name", 
                                                                                                          y = "feature.statistic"), size = 1, color = "black", 
                                                                                               data = tmp_filt) + labs(x = "", y = "Weight (scaled)", 
                                                                                                                       title = "")+ ylim(0,0.01) + coord_flip() + theme(axis.line = element_line(color = "black"), 
                                                                                                                                                                        axis.text.y = element_text(size = rel(0.75), hjust = 1, 
                                                                                                                                                                                                   color = "black"), axis.text.x = element_text(size = rel(1), 
                                                                                                                                                                                                                                                vjust = 0.5, color = "black"), axis.title.y = element_blank(), 
                                                                                                                                                                        legend.position = "none", panel.background = element_blank())
  return(p)
}


plot2 <- function (enrichment.results, factor, alpha = 0.1, max.genes = 5, 
          max.pathways = 10, text_size = 3) 
{
  stopifnot(is.list(enrichment.results))
  stopifnot(length(factor) == 1)
  if (!is.numeric(factor)) {
    if (!factor %in% colnames(enrichment.results$pval)) 
      stop(paste0("No feature set enrichment calculated for ", 
                  factor))
  }
  foo <- reshape2::melt(enrichment.results$feature.statistics[, 
                                                              factor], na.rm = TRUE, value.name = "feature.statistic")
  foo$feature <- rownames(foo)
  feature.sets <- enrichment.results$feature.sets
  feature.sets[feature.sets == 0] <- NA
  bar <- reshape2::melt(feature.sets, na.rm = TRUE)[, c(1, 
                                                        2)]
  colnames(bar) <- c("pathway", "feature")
  bar$pathway <- as.character(bar$pathway)
  bar$feature <- as.character(bar$feature)
  baz <- reshape2::melt(enrichment.results$pval.adj[, factor], 
                        value.name = "pvalue", na.rm = TRUE)
  baz$pathway <- rownames(baz)
  baz <- baz[baz$pvalue <= alpha, , drop = FALSE]
  if (nrow(baz) == 0) {
    stop("No siginificant pathways at the specified alpha threshold. \n\n         For an overview use plot_enrichment_heatmap().")
  }
  else {
    if (nrow(baz) > max.pathways) 
      baz <- head(baz[order(baz$pvalue), ], n = max.pathways)
  }
  baz$pathway <- factor(baz$pathway, levels = baz$pathway[order(baz$pvalue, 
                                                                decreasing = TRUE)])
  foobar <- merge(foo, bar, by = "feature")
  tmp <- merge(foobar, baz, by = "pathway")
  tmp_filt <- top_n(group_by(tmp, pathway), n = max.genes, 
                    abs(feature.statistic))
  pathways <- unique(tmp_filt$pathway)
  df <- data.frame(pathway = pathways, nfeatures = rowSums(feature.sets, 
                                                           na.rm = TRUE)[pathways])
  df <- merge(df, baz, by = "pathway")
  df$pathway_long_name <- sprintf("%s\n (Ngenes = %d) \n (p-val = %0.2g)", 
                                  df$pathway, df$nfeatures, df$pvalue)
  tmp <- merge(tmp, df[, c("pathway", "pathway_long_name")], 
               by = "pathway")
  tmp_filt <- merge(tmp_filt, df[, c("pathway", "pathway_long_name")], 
                    by = "pathway")
  order_pathways <- df$pathway_long_name[order(df$pvalue, decreasing = FALSE)]
  tmp$pathway_long_name <- factor(tmp$pathway_long_name, levels = order_pathways)
  tmp_filt$pathway_long_name <- factor(tmp_filt$pathway_long_name, 
                                       levels = order_pathways)
  p <- ggplot(tmp, aes_string(x = "pathway_long_name", y = "feature.statistic")) + 
    geom_text_repel(aes_string(x = "pathway_long_name", y = "feature.statistic", 
                               label = "feature"), size = text_size, color = "black", 
                    force = 1, data = tmp_filt) + geom_point(size = 0.5, 
                                                             color = "lightgrey") + geom_point(aes_string(x = "pathway_long_name", 
                                                                                                          y = "feature.statistic"), size = 1, color = "black", 
                                                                                               data = tmp_filt) + labs(x = "", y = "Weight (scaled)", 
                                                                                                                       title = "")+ ylim(0,0.01) + coord_flip() + theme(axis.line = element_line(color = "black"), 
                                                                                                                                                          axis.text.y = element_text(size = rel(0.75), hjust = 1, 
                                                                                                                                                                                     color = "black"), axis.text.x = element_text(size = rel(1), 
                                                                                                                                                                                                                                  vjust = 0.5, color = "black"), axis.title.y = element_blank(), 
                                                                                                                                                          legend.position = "none", panel.background = element_blank())
  return(p)
}

# Plot using the modified functions

res_pos <- plot2(
  enrichment.results = res.positive,
  factor = 9, 
  max.pathways = 15,
  max.genes = 5, text_size=4.5
)

ggsave("/MOFA_dir/GSEA_factor9_detailed_pos.pdf",res_pos,width=9,height=10)

res_neg <- plot1(
  enrichment.results = res.negative,
  factor = 9, 
  max.pathways = 15,
  max.genes = 5, text_size=4.5
)
ggsave("/MOFA_dir/GSEA_factor9_detailed_neg.pdf",res_neg,width=9,height=10)


# Extract for converging evidence plot

f9_mRNA <- get_weights(BA9,views="Expr")
  f9_mRNA<-f9_mRNA$Expr
  f9_mRNA <- f9_mRNA[,9]
  f9_mRNA <- sort(f9_mRNA,decreasing = TRUE)


#Meth 
f9_Meth <- get_weights(BA9,views="Meth")
  f9_Meth<-f9_Meth$Meth
  f9_Meth <- f9_Meth[,9]
  f9_Meth <- sort(f9_Meth,decreasing = TRUE)
write.table(names(f9_mRNA),"/MOFA_dir/results_ranking/6_Factor9_mRNA_loadings.txt",row.names = F,col.names = F,quote=F)  
  
  # Export loadings for converging evidence visualization
  
  
  quantile(f9_mRNA,probs=c(0.025,0.25,0.5,0.75,0.975))
  
#        2.5%          25%          50%          75%        97.5% 
# -0.015001708 -0.003626335  0.000563293  0.004574293  0.015167444
  

  quantile(f9_Meth,probs=c(0.025,0.25,0.5,0.75,0.975))
#   2.5%          25%          50%          75%        97.5% 
# -0.145604531 -0.046109412  0.002832227  0.053496722  0.152205286 
  
  f9_mRNA_top <- f9_mRNA[f9_mRNA > 0.015167444 | f9_mRNA < -0.015001708]
write.table(names(f9_mRNA_top),"/zi-flstorage/group_genepi/data/EP/SysMed/Cocaine/BA9_multiome/results_ranking/gene_level/6_Factor9_mRNA_loadings.txt",row.names = F,col.names = F,quote=F)

f9_Meth_top <- f9_Meth[f9_Meth > 0.152205286 | f9_Meth < -0.145604531]
names_meth <- gsub("*...........-.","",names(f9_Meth_top))

# prepare for missMethyl 

f9_Meth_pos <- f9_Meth[f9_Meth > 0.152205286]
f9_Meth_neg <- f9_Meth[f9_Meth < -0.145604531]

names_f9_Meth_pos <- gsub(" -.*","",names(f9_Meth_pos))
names_f9_Meth_neg <- gsub(" -.*","",names(f9_Meth_neg))
names_meth_all <- gsub(" -.*","",names(f9_Meth))

library(stringr)
names_meth <- unique(unlist(str_split(names_meth,";")))
write.table(names_meth,"/MOFA_dir/results_ranking/7_Factor9_meth_loadings.txt",row.names = F,col.names = F,quote=F)

# GO using missMethyl
library(readr)
library(data.table)
library(dplyr)
library(missMethyl)
library(IlluminaHumanMethylationEPICanno.ilm10b2.hg19)
library(IlluminaHumanMethylationEPICanno.ilm10b4.hg19)
library(ggplot2)
library(cowplot)

go_res_pos <- gometh(names_f9_Meth_pos, names_meth_all, "GO", "EPIC", T,sig.genes = T)
go_res_pos <- go_res_pos[order(go_res_pos$P.DE),]
write.table(go_res_pos,"/MOFA_dir/f9_meth_GO_pos.txt",row.names = F,col.names = F,quote=F,sep=";")

go_res_neg <- gometh(names_f9_Meth_neg, names_meth_all, "GO", "EPIC", T,sig.genes = T)
go_res_neg <- go_res_neg[order(go_res_neg$P.DE),]
write.table(go_res_neg,"/MOFA_dir/f9_meth_GO_neg.txt",row.names = F,col.names = F,quote=F,sep=";")

# plot top GO terms
up_table <- go_res_pos[,c("TERM","P.DE")][c(1:15),]
up_table$P.DE <- -log10(up_table$P.DE)
position1 <- rev(up_table$TERM)

p1 <- ggplot(data = up_table, aes(x = P.DE, y = TERM)) + geom_point(size=3,color="#E43F3F") +theme_bw() + ylab("") + xlab("-log10(p)") + scale_y_discrete(limits = position1)+xlim(2,3.7)
ggsave("/MOFA_dir/output/GO_factor9_meth_pos_weights.pdf",p1,width=8,height=4)

down_table <- go_res_neg[,c("TERM","P.DE")][c(1:15),]
down_table$P.DE <- -log10(down_table$P.DE)
position2 <- rev(down_table$TERM)

p2 <- ggplot(data = down_table, aes(x = P.DE, y = TERM)) + geom_point(size=3,color="#268989") +theme_bw() + ylab("") + xlab("-log10(p)") + scale_y_discrete(limits = position2)+xlim(2,3.7) 
ggsave("/MOFA_dir/output/GO_factor9_meth_neg_weights.pdf",p2,width=8,height=4)

# Plot GO term panel 

library(cowplot)
pdf("/MOFA_dir/output/GO_meth_f9_panel.pdf",width=14,height=4)
plot_grid(p1,p2,ncol=2,align="v")
dev.off()

```
